Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
sec 4 updates

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
   \caption{Evaluation of the correlation between the RV's and the asymmetry parameters when a faculae is present on the photosphere of the star. In this case both the shape and the width of the CCF changes as the faculae moves, producing statistically significative correlations between the RV's and respectively the asymmetry parameter and the width parameter.}
    \label{fig:faculae.corr}
\end{center}
\end{figure*}

>>>>

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
   \caption{Using CCFs from SOAP 2.0 with a single facula, the correlation between the estimated RV's and the asymmetry parameters are displayed. In this case both the shape and the width of the CCF changes as the facula moves, producing statistically significant correlations between the estimated RV's and, respectively, the asymmetry parameter or the width parameter.}
    \label{fig:faculae.corr}
\end{center}
\end{figure*}
